Finite element analysis of multi-dimensional and simplified models for beams

### 2024-04-19 final_seminar/main.tex
final

% Redefine the title page template
\setbeamertemplate{title page}{
    \begin{center}
        \usebeamercolor[fg]{titlegraphic}\inserttitlegraphic\par
        \vskip0.25em%
        {\fontsize{14}{16}\selectfont\usebeamerfont{title}\usebeamercolor[fg]{title}\inserttitle\par}% Increase the font size of the title
        \ifx\insertsubtitle\@empty%
        \else%
        \vskip0.25em%
        {\fontsize{12}{14}\selectfont\usebeamerfont{subtitle}\usebeamercolor[fg]{subtitle}\insertsubtitle\par}% Increase the font size of the subtitle
        \fi%     
        \vskip1em\par
        \usebeamerfont{author}\insertauthor\par
        \vskip1em\par
        \usebeamerfont{institute}\insertinstitute\par
        \vskip1em%
        \includegraphics[width=0.2\linewidth]{logo-up.jpg}\par % Include the logo here
        \vskip1em\par
        \usebeamerfont{date}\insertdate\par
        \vfill
    \end{center}
}

@@

            \only<3>{
            \textbf{General vibration problem:}

@@

            \only<4->{
            \textbf{General vibration problem:}

            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
            \begin{eqnarray}
                c(u''(t),v)+b(u(t),v) = (f(t),v) \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
            \end{eqnarray}
            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.}

@@

            \only<2->{
                \textbf{Conclusion for the Timoshenko beam model:}
                \begin{itemize}
                    \item The Timoshenko beam model compares well with the two-dimensional beam model.
                    \item The shape of the beam influences how well the Timoshenko beam model compares to the two-dimensional beam model.
                    \item The results of the article are confirmed.
                    \item The case of a height to length ration of 1 to 20 is the best case we have tested.
                \end{itemize}
            }

@@

    \subsection{Validity of the Two-dimensional beam model}
        \begin{frame}{Validity of the Two-dimensional beam model}
            \begin{center}
                \begin{minipage}[b]{0.45\linewidth}
                    \centering
                    \begin{tikzpicture}[scale=0.6]
                        \draw[line width = 0.3mm] (-0.1,1) -- (6.9,1);
                        \draw[line width = 0.3mm] (-0.1,-1) -- (6.9,-1);
                        \draw[line width = 0.3mm] (6.9,-1) -- (6.9,1);
                        \draw[line width = 0.3mm] (-0.1,-1) -- (-0.1,1);

@@

        \begin{frame}{Three-Dimensional model vs Two-Dimensional model}
            \centering
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{3D12.png}
                \\ 3D Beam Type - $\lambda_{12} = 2.3293$
                \label{fig:minipage2}
            \end{minipage}
            \hfill
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{2D3.png}
                \\ 2D Beam Type - $\lambda_3 = 2.3273$
                \label{fig:minipage1}
            \end{minipage}

@@

        \begin{frame}{Three-Dimensional model}
            \centering
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{3D33.png}
                \\ 3D Non-Beam Type - $\lambda_{33} = 69.374$
                \label{fig:minipage6}
            \end{minipage}
            \hfill
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{2D8.png}
                \\ 2D Non-Beam Type - $\lambda_8 = 69.344$
                \label{fig:minipage5}
            \end{minipage}

@@

        \begin{frame}{}

        \begin{frame}
            \begin{table}[htbp]
                \scalebox{.8}{
                \makebox[\textwidth]{
                    \begin{tabular}{|cc|cc|cc|cc||cc|}
                        \hline
                        \multicolumn{10}{|c|}{Comparsion of Eigenvalues with $h = 1/5$, with decreasing $b$ and $b < h$.} \\
                        \hline
                        \hline
                        i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
                        \hline
                        {2} & 0.12307 & {2} & 0.12234 & {2} & 0.12198 & {3} & 0.12178 & 1     & 0.12151 \\
                        {3} & 3.5773 & {5} & 3.5630 & {6} & 3.5558 & {8} & 3.5519 & 2     & 3.5460 \\
                        \rowcolor{lightgray}{5} & 7.7799 & {6} & 7.7596 & {8} & 7.7471 & {11} & 7.7401 & 3     & 7.7311 \\
                        {8} & 20.334 & {9} & 20.283 & {11} & 20.26 & {14} & 20.247 & 4     & 20.225 \\
                        {10} & 56.247 & {12} & 56.173 & {15} & 56.156 & {22} & 56.142 & 5     & 56.109 \\
                        \rowcolor{lightgray}{11} & 69.197 & {14} & 69.319 & {17} & 69.281 & {24} & 69.238 & 6     & 69.164 \\
                        {14} & 114.03 & {16} & 114.01 & {20} & 114.05 & {29} & 114.06 & 7     & 114.03 \\
                        \rowcolor{lightgray}{17} & 187.01 & {19} & 189.14 & {25} & 189.37 & {36} & 189.34 & 8     & 189.17 \\
                        {18} & 192.21 & {20} & 192.41 & {26} & 192.58 & {37} & 192.63 & 9     & 192.61 \\
                        {21} & 284.76 & {23} & 285.43 & {31} & 285.74 & {42} & 285.84 & 10    & 285.85 \\
                        {23} & 327.57 & {26} & 328.24 & {35} & 328.37 & {46} & 328.40 & 11    & 328.40 \\
                        \rowcolor{lightgray}{25} & 347.77 & {28} & 356.44 & {36} & 357.30 & {50} & 357.33 & 12    & 357.08 \\
                        {27} & 393.69 & {30} & 396.84 & {38} & 397.28 & {53} & 397.37 & 13    & 397.33 \\
                        {30} & 434.46 & {34} & 441.05 & {41} & 441.81 & {57} & 441.99 & 14    & 442.00 \\
                        \rowcolor{lightgray}{31} & 523.65 & {36} & 534.04 & {43} & 534.17 & {63} & 534.03 & 15    & 533.71 \\
                        {34} & 550.51 & {37} & 537.82 & {44} & 538.86 & {64} & 539.06 & 16    & 538.97 \\
                        \rowcolor{lightgray}{37} & 590.86 & {41} & 587.43 & {48} & 594.17 & {65} & 595.58 & 17    & 596.06 \\
                        {39} & 590.86 & {42} & 600.52 & {49} & 602.25 & {67} & 602.69 & 18    & 602.77 \\
                        \rowcolor{lightgray}{42} & 646.21 & {44} & 657.22 & {50} & 658.04 & {71} & 658.06 & 19    & 657.87 \\
                        {44} & 711.07 & {46} & 714.62 & {53} & 717.10 & {73} & 717.51 & 20    & 717.37 \\
                        \hline
                        \hline
                        \multicolumn{2}{|c|}{Max RE: \  2.6069\%} &\multicolumn{2}{c|}{Max RE: \ 1.4469\%}  & \multicolumn{2}{c|}{Max RE: \  0.38192\%}  & \multicolumn{2}{c||}{Max RE: \ 0.22301\%}& \multicolumn{2}{c|}{-} \\
                        \hline
                    \end{tabular}%
                    \label{tab:2v3_1}%
                }}
            \end{table}%
        \end{frame}

        \begin{frame}
            \begin{table}[htbp]
                \centering
                \begin{tabular}{|c|cccc|}
                    \hline
                    \multicolumn{5}{|c|}{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/5$.} \\
                    \hline
                    \hline
                    & {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
                    \hline
                    Beam Type & 2.1420 \% & 0.6804 \% & 0.38192 \% & 0.22301 \% \\
                    Non-Beam Type & 2.6069 \% & 1.4469 \% & 0.31546 \% & 0.11680 \% \\
                    \hline
                \end{tabular}%
                \label{tab:2Dv3D_1_breakup}%
            \end{table}%
        \end{frame}

        \begin{frame}
            \begin{table}[ht]
                \scalebox{.8}{
                \makebox[\textwidth]{
                \begin{tabular}{|cc|cc|cc|cc||cc|}
                    \hline
                    \multicolumn{10}{|c|}{Comparsion of Eigenvalues with $h = 1/20$, with decreasing $b$ and $b < h$.} \\
                    \hline
                    \hline
                    i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
                    \hline
                    {2} & 0.008043 & {2} & 0.008029 & {2} & 0.008023 & {3} & 0.00802 & {1} & {0.008013} \\
                    {3} & 0.3087 & {4} & 0.30816 & {5} & 0.30794 & {7} & 0.30785 & {2} & {0.30757} \\
                    {5} & 2.3357 & {8} & 2.3316 & {9} & 2.3300  & {12} & 2.3293 & {3} & {2.3273} \\
                    \rowcolor{lightgray}{8} & 7.7217 & {10} & 7.7156 & {13} & 7.7124 & {16} & 7.7111 & {4} & {7.7077} \\
                    {10} & 8.5387 & {11} & 8.5238 & {14} & 8.5182 & {18} & 8.516 & {5} & {8.5086} \\
                    {11} & 21.986 & {14} & 21.948 & {18} & 21.934 & {24} & 21.929 & {6} & {21.911} \\
                    {14} & 45.863 & {18} & 45.781 & {21} & 45.756 & {30} & 45.746 & {7} & {45.712} \\
                    \rowcolor{lightgray}{17} & 69.444 & {19} & 69.408 & {25} & 69.385 & {33} & 69.374 & {8} & {69.344} \\
                    {18} & 83.149 & {22} & 82.999 & {27} & 82.960 & {36} & 82.944 & {9} & {82.887} \\
                    {21} & 136.44 & {25} & 136.19 & {31} & 136.14 & {42} & 136.12 & {10} & {136.03} \\
                    \rowcolor{lightgray}{23} & 192.62 & {27} & 192.62 & {35} & 192.58 & {47} & 192.56 & {11} & {192.48} \\
                    {25} & 207.87 & {29} & 207.5 & {36} & 207.43 & {48} & 207.41 & {12} & {207.29} \\
                    {27} & 299.14 & {33} & 298.63 & {41} & 298.56 & {55} & 298.53 & {13} & {298.38} \\
                    \rowcolor{lightgray}{30} & 376.68 & {35} & 377.01 & {44} & 377.01 & {58} & 376.98 & {14} & {376.83} \\
                    {31} & 411.58 & {37} & 410.89 & {46} & 410.83 & {61} & 410.81 & {15} & {410.63} \\
                    {34} & 546.15 & {40} & 545.27 & {50} & 545.24 & {66} & 545.23 & {16} & {545.03} \\
                    \rowcolor{lightgray}{37} & 620.77 & {42} & 622.02 & {53} & 622.19 & {69} & 622.18 & {17} & {621.95} \\
                    {39} & 703.55 & {44} & 702.49 & {54} & 702.29 & {71} & 702.53 & {18} & {702.31} \\
                    {42} & 884.27 & {47} & 883.02 & {59} & 883.14 & {82} & 883.19 & {19} & {882.96} \\
                    \rowcolor{lightgray}{44} & 923.68 & {49} & 926.88 & {60} & 927.43 & {86} & 927.50 & {20} & {927.18} \\
                    \hline
                    \hline
                    \multicolumn{2}{|c|}{Max RE: \  0.37701\%} &\multicolumn{2}{c|}{Max RE: \ 0.19893\%}  & \multicolumn{2}{c|}{Max RE: \  0.12393\%}  & \multicolumn{2}{c||}{Max RE: \ 0.092843\%}& \multicolumn{2}{c|}{-} \\
                    \hline
                \end{tabular}%
                \label{tab:2v3_2}%
            }}
            \end{table}%
        \end{frame}

        \begin{frame}
            \begin{table}[htbp]
                \centering
                \begin{tabular}{|c|cccc|}
                    \hline
                    \multicolumn{5}{|c|}{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$} \\
                    \hline
                    \hline
                    & {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
                    \hline
                    Beam Type & 0.37701 \% & 0.19893 \% & 0.12393 \% & 0.092843 \% \\
                    Non-Beam Type & 0.37682 \% & 0.10218 \% & 0.061213 \% & 0.043601 \% \\
                    \hline
                \end{tabular}%
                \label{tab:2v3_2_split}%
            \end{table}%
        \end{frame}

        \begin{frame}
            \begin{table}[htbp]
                \scalebox{.8}{
                \makebox[\textwidth]{
                    \begin{tabular}{|cc|cc|cc||cc|}
                        \hline
                        \multicolumn{8}{|c|}{Comparsion of Eigenvalues with $h = 1/20$, with increasing $b$ and $b > h$} \\
                        \hline
                        \hline
                        i     & {b = 2h} & i     & {b = 4h} & i     & {b = 8h} & j     & 2D \\
                        \hline
                        {2} & 0.008076 & {1} & 0.008162 & {1} & 0.008324 & 1     & 0.008013 \\
                        {3} & 0.30995 & {3} & 0.31298 & {3} & 0.31738 & 2     & 0.30757 \\
                        {5} & 2.3462 & {5} & 2.3737 & {6} & 2.4116 & 3     & 2.3273 \\
                        \rowcolor{lightgray}{8} & 7.7312 & {8} & 7.7471 & {9} & 7.7711 & 4     & 7.7077 \\
                        {10} & 8.5841 & {9} & 8.7082 & {10} & 8.7929 & 5     & 8.5086 \\
                        {11} & 22.124 & {12} & 22.491 & {14} & 23.222 & 6     & 21.911 \\
                        {14} & 46.195 & {14} & 47.003 & {18} & 47.921 & 7     & 45.712 \\
                        \rowcolor{lightgray}{17} & 69.454 & {17} & 69.281 & {22} & 72.307 & 8     & 69.344 \\
                        {18} & 83.822 & {18} & 85.218 & {24} & 80.607 & 9     & 82.887 \\
                        {21} & 137.43 & {21} & 138.58 & {32} & 140.97 & 10    & 136.03 \\
                        \hline
                        \hline
                        \multicolumn{2}{|c|}{Max RE: \  1.1289\%} &\multicolumn{2}{c|}{Max RE: \ 2.8261\%}  & \multicolumn{2}{c|}{Max RE: \  5.9821\%} & \multicolumn{2}{c|}{-} \\
                        \hline
                    \end{tabular}%
                    \label{tab:b>h_20}%
                }}
            \end{table}
        \end{frame}

        \begin{frame}
            \begin{table}[htbp]
                \centering
                \begin{tabular}{|c|ccc|}
                    \hline
                    \multicolumn{4}{|c|}{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$} \\
                    \hline
                    \hline
                    & {b = 2h} & {b = 4h} & {b = 8h} \\
                    \hline
                    Beam Type & 1.1289 \% & 2.8261 \% & 5.9821 \% \\
                    Non-Beam Type & 0.30521 \% & 0.51096 \% & 4.2734 \% \\
                    \hline
                \end{tabular}%
                \label{tab:b>h-split_20}%
            \end{table}%
        \end{frame}

\section{Conclusion}
    \begin{frame}{Conclusion}
        \begin{itemize}
            \item 
        \end{itemize}

        \textbf{Future Work:}
        \begin{itemize}
            \item Include damping in the models.
        \end{itemize}

>>>>

% Redefine the title page template
\setbeamertemplate{title page}{
    \begin{center}
        \usebeamercolor[fg]{titlegraphic}\inserttitlegraphic\par
        \vskip0.25em%
        {\fontsize{14}{16}\selectfont\usebeamerfont{title}\usebeamercolor[fg]{title}\inserttitle\par}% Increase the font size of the title
        \ifx\insertsubtitle\@empty%
        \else%
        \vskip0.25em%
        {\fontsize{12}{14}\selectfont\usebeamerfont{subtitle}\usebeamercolor[fg]{subtitle}\insertsubtitle\par}% Increase the font size of the subtitle
        \fi%     
        \vskip1em\par
        \usebeamerfont{author}\insertauthor\par
        \vskip1em\par
        \usebeamerfont{institute}\insertinstitute\par
        \vskip1em%
        \includegraphics[width=0.4\linewidth]{logo-up.jpg}\par % Include the logo here
        \vskip1em\par
        \usebeamerfont{date}\insertdate\par
        \vfill
    \end{center}
}

@@

            \only<3->{
            \textbf{General vibration problem:}

@@

@@

            \only<2->{
                \textbf{Conclusion for the Timoshenko beam model:}
                \begin{itemize}
                    \item The Timoshenko beam model compares well with the two-dimensional beam model. It is a suitable model to use instead of the two-dimensional beam model.
                    \item The shape of the beam influences how well the Timoshenko beam model compares to the two-dimensional beam model.
                    \item The results of the article are confirmed.
                \end{itemize}
            }

@@

    \subsection{Validity of the Two-dimensional beam}
        \begin{frame}{Validity of the Two-dimensional beam - Visual representation}
            \begin{center}
                \begin{minipage}[b]{0.45\linewidth}
                    \centering
                    \begin{tikzpicture}[scale=0.6]
                        \draw[line width = 0.3mm] (-0.1,1) -- (6.9,1);
                        \draw[line width = 0.3mm] (-0.1,-1) -- (6.9,-1);
                        \draw[line width = 0.3mm] (6.9,-1) -- (6.9,1);
                        \draw[line width = 0.3mm] (-0.1,-1) -- (-0.1,1);

@@

        \begin{frame}{Validity of the Two-dimensional beam- Beam type mode shapes}
            \centering
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{3D12.png}
                \\ 3D Beam Type - $\lambda_{12} = 2.3293$
                \label{fig:minipage2}
            \end{minipage}
            \hfill
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{2D3.png}
                \\ 2D Beam Type - $\lambda_3 = 2.3273$
                \label{fig:minipage1}
            \end{minipage}

@@

        \begin{frame}{Validity of the Two-dimensional beam - Non-beam type mode shapes}
            \centering
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{3D33.png}
                \\ 3D Non-Beam Type - $\lambda_{33} = 69.374$
                \label{fig:minipage6}
            \end{minipage}
            \hfill
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{2D8.png}
                \\ 2D Non-Beam Type - $\lambda_8 = 69.344$
                \label{fig:minipage5}
            \end{minipage}

@@

        \begin{frame}{Validity of the Two-dimensional beam - Comparison short thick beam}
            \begin{table}[htbp]
                \scalebox{.8}{
                \makebox[\textwidth]{
                    \begin{tabular}{|cc|cc|cc|cc||cc|}
                        \hline
                        \multicolumn{10}{|c|}{Comparsion of Eigenvalues with $h = 1/5$, with decreasing $b$ and $b < h$.} \\
                        \hline
                        \hline
                        i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
                        \hline
                        {2} & 0.12307 & {2} & 0.12234 & {2} & 0.12198 & {3} & 0.12178 & 1     & 0.12151 \\
                        {3} & 3.5773 & {5} & 3.5630 & {6} & 3.5558 & {8} & 3.5519 & 2     & 3.5460 \\
                        \rowcolor{lightgray}{5} & 7.7799 & {6} & 7.7596 & {8} & 7.7471 & {11} & 7.7401 & 3     & 7.7311 \\
                        {8} & 20.334 & {9} & 20.283 & {11} & 20.26 & {14} & 20.247 & 4     & 20.225 \\
                        {10} & 56.247 & {12} & 56.173 & {15} & 56.156 & {22} & 56.142 & 5     & 56.109 \\
                        \rowcolor{lightgray}{11} & 69.197 & {14} & 69.319 & {17} & 69.281 & {24} & 69.238 & 6     & 69.164 \\
                        {14} & 114.03 & {16} & 114.01 & {20} & 114.05 & {29} & 114.06 & 7     & 114.03 \\
                        \rowcolor{lightgray}{17} & 187.01 & {19} & 189.14 & {25} & 189.37 & {36} & 189.34 & 8     & 189.17 \\
                        {18} & 192.21 & {20} & 192.41 & {26} & 192.58 & {37} & 192.63 & 9     & 192.61 \\
                        {21} & 284.76 & {23} & 285.43 & {31} & 285.74 & {42} & 285.84 & 10    & 285.85 \\
                        {23} & 327.57 & {26} & 328.24 & {35} & 328.37 & {46} & 328.40 & 11    & 328.40 \\
                        \rowcolor{lightgray}{25} & 347.77 & {28} & 356.44 & {36} & 357.30 & {50} & 357.33 & 12    & 357.08 \\
                        {27} & 393.69 & {30} & 396.84 & {38} & 397.28 & {53} & 397.37 & 13    & 397.33 \\
                        {30} & 434.46 & {34} & 441.05 & {41} & 441.81 & {57} & 441.99 & 14    & 442.00 \\
                        \rowcolor{lightgray}{31} & 523.65 & {36} & 534.04 & {43} & 534.17 & {63} & 534.03 & 15    & 533.71 \\
                        {34} & 550.51 & {37} & 537.82 & {44} & 538.86 & {64} & 539.06 & 16    & 538.97 \\
                        \rowcolor{lightgray}{37} & 590.86 & {41} & 587.43 & {48} & 594.17 & {65} & 595.58 & 17    & 596.06 \\
                        {39} & 590.86 & {42} & 600.52 & {49} & 602.25 & {67} & 602.69 & 18    & 602.77 \\
                        \rowcolor{lightgray}{42} & 646.21 & {44} & 657.22 & {50} & 658.04 & {71} & 658.06 & 19    & 657.87 \\
                        {44} & 711.07 & {46} & 714.62 & {53} & 717.10 & {73} & 717.51 & 20    & 717.37 \\
                        \hline
                        \hline
                        \multicolumn{2}{|c|}{Max RE: \  2.6069\%} &\multicolumn{2}{c|}{Max RE: \ 1.4469\%}  & \multicolumn{2}{c|}{Max RE: \  0.38192\%}  & \multicolumn{2}{c||}{Max RE: \ 0.22301\%}& \multicolumn{2}{c|}{-} \\
                        \hline
                    \end{tabular}%
                    \label{tab:2v3_1}%
                }}
            \end{table}%
        \end{frame}

        \begin{frame}{Validity of the Two-dimensional beam - Comparison short thick beam}
            \begin{table}[htbp]
                \centering
                \begin{tabular}{|c|cccc|}
                    \hline
                    \multicolumn{5}{|c|}{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/5$.} \\
                    \hline
                    \hline
                    & {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
                    \hline
                    Beam Type & 2.1420 \% & 0.6804 \% & 0.38192 \% & 0.22301 \% \\
                    Non-Beam Type & 2.6069 \% & 1.4469 \% & 0.31546 \% & 0.11680 \% \\
                    \hline
                \end{tabular}%
                \label{tab:2Dv3D_1_breakup}%
            \end{table}%
        \end{frame}

        \begin{frame}{Validity of the Two-dimensional beam - Comparison long slender beam}
            \begin{table}[ht]
                \scalebox{.8}{
                \makebox[\textwidth]{
                \begin{tabular}{|cc|cc|cc|cc||cc|}
                    \hline
                    \multicolumn{10}{|c|}{Comparsion of Eigenvalues with $h = 1/20$, with decreasing $b$ and $b < h$.} \\
                    \hline
                    \hline
                    i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
                    \hline
                    {2} & 0.008043 & {2} & 0.008029 & {2} & 0.008023 & {3} & 0.00802 & {1} & {0.008013} \\
                    {3} & 0.3087 & {4} & 0.30816 & {5} & 0.30794 & {7} & 0.30785 & {2} & {0.30757} \\
                    {5} & 2.3357 & {8} & 2.3316 & {9} & 2.3300  & {12} & 2.3293 & {3} & {2.3273} \\
                    \rowcolor{lightgray}{8} & 7.7217 & {10} & 7.7156 & {13} & 7.7124 & {16} & 7.7111 & {4} & {7.7077} \\
                    {10} & 8.5387 & {11} & 8.5238 & {14} & 8.5182 & {18} & 8.516 & {5} & {8.5086} \\
                    {11} & 21.986 & {14} & 21.948 & {18} & 21.934 & {24} & 21.929 & {6} & {21.911} \\
                    {14} & 45.863 & {18} & 45.781 & {21} & 45.756 & {30} & 45.746 & {7} & {45.712} \\
                    \rowcolor{lightgray}{17} & 69.444 & {19} & 69.408 & {25} & 69.385 & {33} & 69.374 & {8} & {69.344} \\
                    {18} & 83.149 & {22} & 82.999 & {27} & 82.960 & {36} & 82.944 & {9} & {82.887} \\
                    {21} & 136.44 & {25} & 136.19 & {31} & 136.14 & {42} & 136.12 & {10} & {136.03} \\
                    \rowcolor{lightgray}{23} & 192.62 & {27} & 192.62 & {35} & 192.58 & {47} & 192.56 & {11} & {192.48} \\
                    {25} & 207.87 & {29} & 207.5 & {36} & 207.43 & {48} & 207.41 & {12} & {207.29} \\
                    {27} & 299.14 & {33} & 298.63 & {41} & 298.56 & {55} & 298.53 & {13} & {298.38} \\
                    \rowcolor{lightgray}{30} & 376.68 & {35} & 377.01 & {44} & 377.01 & {58} & 376.98 & {14} & {376.83} \\
                    {31} & 411.58 & {37} & 410.89 & {46} & 410.83 & {61} & 410.81 & {15} & {410.63} \\
                    {34} & 546.15 & {40} & 545.27 & {50} & 545.24 & {66} & 545.23 & {16} & {545.03} \\
                    \rowcolor{lightgray}{37} & 620.77 & {42} & 622.02 & {53} & 622.19 & {69} & 622.18 & {17} & {621.95} \\
                    {39} & 703.55 & {44} & 702.49 & {54} & 702.29 & {71} & 702.53 & {18} & {702.31} \\
                    {42} & 884.27 & {47} & 883.02 & {59} & 883.14 & {82} & 883.19 & {19} & {882.96} \\
                    \rowcolor{lightgray}{44} & 923.68 & {49} & 926.88 & {60} & 927.43 & {86} & 927.50 & {20} & {927.18} \\
                    \hline
                    \hline
                    \multicolumn{2}{|c|}{Max RE: \  0.37701\%} &\multicolumn{2}{c|}{Max RE: \ 0.19893\%}  & \multicolumn{2}{c|}{Max RE: \  0.12393\%}  & \multicolumn{2}{c||}{Max RE: \ 0.092843\%}& \multicolumn{2}{c|}{-} \\
                    \hline
                \end{tabular}%
                \label{tab:2v3_2}%
            }}
            \end{table}%
        \end{frame}

        \begin{frame}{Validity of the Two-dimensional beam - Comparison long slender beam}
            \begin{table}[htbp]
                \centering
                \begin{tabular}{|c|cccc|}
                    \hline
                    \multicolumn{5}{|c|}{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$} \\
                    \hline
                    \hline
                    & {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
                    \hline
                    Beam Type & 0.37701 \% & 0.19893 \% & 0.12393 \% & 0.092843 \% \\
                    Non-Beam Type & 0.37682 \% & 0.10218 \% & 0.061213 \% & 0.043601 \% \\
                    \hline
                \end{tabular}%
                \label{tab:2v3_2_split}%
            \end{table}%
        \end{frame}

        \begin{frame}{Validity of the Two-dimensional beam - depth larger than height}
            \begin{table}[htbp]
                \scalebox{.8}{
                \makebox[\textwidth]{
                    \begin{tabular}{|cc|cc|cc||cc|}
                        \hline
                        \multicolumn{8}{|c|}{Comparsion of Eigenvalues with $h = 1/20$, with increasing $b$ and $b > h$} \\
                        \hline
                        \hline
                        i     & {b = 2h} & i     & {b = 4h} & i     & {b = 8h} & j     & 2D \\
                        \hline
                        {2} & 0.008076 & {1} & 0.008162 & {1} & 0.008324 & 1     & 0.008013 \\
                        {3} & 0.30995 & {3} & 0.31298 & {3} & 0.31738 & 2     & 0.30757 \\
                        {5} & 2.3462 & {5} & 2.3737 & {6} & 2.4116 & 3     & 2.3273 \\
                        \rowcolor{lightgray}{8} & 7.7312 & {8} & 7.7471 & {9} & 7.7711 & 4     & 7.7077 \\
                        {10} & 8.5841 & {9} & 8.7082 & {10} & 8.7929 & 5     & 8.5086 \\
                        {11} & 22.124 & {12} & 22.491 & {14} & 23.222 & 6     & 21.911 \\
                        {14} & 46.195 & {14} & 47.003 & {18} & 47.921 & 7     & 45.712 \\
                        \rowcolor{lightgray}{17} & 69.454 & {17} & 69.281 & {22} & 72.307 & 8     & 69.344 \\
                        {18} & 83.822 & {18} & 85.218 & {24} & 80.607 & 9     & 82.887 \\
                        {21} & 137.43 & {21} & 138.58 & {32} & 140.97 & 10    & 136.03 \\
                        \hline
                        \hline
                        \multicolumn{2}{|c|}{Max RE: \  1.1289\%} &\multicolumn{2}{c|}{Max RE: \ 2.8261\%}  & \multicolumn{2}{c|}{Max RE: \  5.9821\%} & \multicolumn{2}{c|}{-} \\
                        \hline
                    \end{tabular}%
                    \label{tab:b>h_20}%
                }}
            \end{table}
        \end{frame}

        \begin{frame}{Validity of the Two-dimensional beam - depth larger than height}
            \begin{table}[htbp]
                \centering
                \begin{tabular}{|c|ccc|}
                    \hline
                    \multicolumn{4}{|c|}{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$} \\
                    \hline
                    \hline
                    & {b = 2h} & {b = 4h} & {b = 8h} \\
                    \hline
                    Beam Type & 1.1289 \% & 2.8261 \% & 5.9821 \% \\
                    Non-Beam Type & 0.30521 \% & 0.51096 \% & 4.2734 \% \\
                    \hline
                \end{tabular}%
                \label{tab:b>h-split_20}%
            \end{table}%
        \end{frame}

        \begin{frame}{Conclusion for the Two-dimensional model}
            \textbf{Conclusion for the Two-dimensional model:}
            \begin{itemize}
                \item The two-dimensional model compares well with the three-dimensional model, given that the depth of the beam is not larger than the height.
                \item Again a long and slender beam does compare better than a short and thick beam.
                \item For body shapes where the depth is larger than the height, the two-dimensional model is not a good approximation to the three-dimensional model and another model should be considered.
            \end{itemize}
        \end{frame}

\section{Conclusion}
    \begin{frame}{Conclusion}
        \textbf{What we have done:}
        \begin{itemize}
            \item Gave a summary of two articles, one that formed the basis of the comparison that we investigated
            \item Presented three different models of a beam, each a different dimension.
            \item Mentioned the well-posedness of the models.
            \item Briefly discussed modal analysis, and how it can be used to compare the models.
            \item Discussed at the validity of the Timoshenko beam model as part of the literature of the first article.
            \item Extended the investigation to the validity of the two-dimensional beam model.
        \end{itemize}

    \end{frame}
    \begin{frame}{Conclusion}
        \textbf{Conclusion}
        \begin{itemize}
            \item Discussed and verified the results of the article.
            \item Shown that the Timoshenko cantilever beam model is a good approximation to the two-dimensional cantilever beam.
            \item Shown that the two-dimensional cantilever beam is a good approximation to the three-dimensional cantilever beam.
            \item Shown that shape of the beams are very important to how well the models compare. The shapes that we looked at can be considered realistic beam shapes that is used in applications.
        \end{itemize}

        \textbf{Future Work:}
        \begin{itemize}
            \item Include damping in the models.
            \item Expand to plate models (this is done in my masters)
            \item Investigate the effect of different distrubances on the models.
        \end{itemize}
    \end{frame}
